---
title       : Welcome to BC Liquor Store 
subtitle    : Developing Data Product Project
author      : Jennifer Yueh
job         : 
logo        : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : default      # 
widgets     : [mathjaz, quiz, bootstrap, shiny, interactive]           
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets: {rCharts: [libraries/nvd3]}
--- 



<style>
  bgclass {
    background-color: #ffff11;
  }

  table.mytable {
    border: 3px solid #7B8273;
    width: 100%;
    /* border-collapse: collapse; *
    font-size: 9px;
    line-height: 50px;
    font-family: 'Trebuchet MS';
    font-weight: bolder;
    color: red;
  }
  table.mytable td {
    font-size: 8px;
  }

</style>







```{r setup, include=FALSE}
# set global chunk options
library(slidify); library(xtable); library(knitr)
opts_chunk$set(cache=FALSE)
```




## <h1 style="text-align:center;font-weight:bold">Introduction</h1> 
<br>
<br>
This shiny application aims to help you get a quick glimpse of your <b>product inventory</b> through the power of Shiny's automatic UI updates. 

<br>
It has two main features:

* <b>User friendly input controls </b>
* <b>Instant and reative output</b>




--- &twocol table.mytable


## <h1 style="text-align:center;font-weight:bold">Input Controls</h1> 
<br>

*** =left
### You decide where to look by ...

* Setting price range by moving the slider or 
* Picking product type: WINE, BEER, SPIRITS or REFRESHMENT
* Selecting country of origin from the drop down list



*** =right

### Our app searches through the data ...
```{r, results="asis", echo=FALSE}
mydf <- readRDS("alcohol.rds")
print(xtable(mydf[1:6, c(1,2,4)]), type="html", html.table.attributes='class:mytable')
```



--- &twocol 


## <h1 style="text-align:center;  font-weight:bold">Instant and reactive output</h1> 
<br>

*** =left

### Notice how ...
* All the related data are automatically re-evaluated and refreshed
* Simply click a tab such as Plot or Tally to see corresponding histogram and data display based on your search criteria


*** =right
### An output plot
```{r alcohol_hist, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3, fig.width=6}
library(dplyr)
library(ggplot2)


thedf <- mydf %>% filter(Price < 30, Price > 5, Type == "WINE", Country == "CANADA")

thestart <- min(thedf$Alcohol_Content)
theend <- max(thedf$Alcohol_Content)
thestep <- ifelse((theend - thestart) >= 2, 2, 0.1)

avgMsg <- paste("Average alcohol content within your search criteria is ", round(mean(thedf$Alcohol_Content),2))

ggplot(thedf, aes(Alcohol_Content)) +
    geom_histogram(fill="lightblue", colour ="slateblue4", bins=25) + 
    
    ggtitle("Histogram of Alcohol Content") + ylab("Count") +
    theme(plot.title=element_text(size=rel(1.5),face="bold")) + 
    
    scale_x_continuous(breaks=seq(thestart, theend, thestep)) +
    
    theme(axis.text=element_text(size=12),
          axis.title=element_text(size=14,face="bold")) +
    geom_vline(xintercept= mean(thedf$Alcohol_Content), col="salmon", size=1) + 
    annotate("text", x=-Inf, y=Inf, label=avgMsg, hjust=-.2, vjust=3, label=avgMsg)
```



```{r echo=FALSE, warning=FALSE, message=FALSE, fig.height=3, fig.width=6}
df <- ddply(thedf, c("Country", "Type", "Subtype"), summarise, 
                    AVG_PRICE=mean(Price, na.rm=TRUE), MIN_PRICE=min(Price, na.rm=TRUE), 
                    MAX_PRICE=max(Price, na.rm=TRUE), AVG_ALCOHOL_CONTENT=mean(Alcohol_Content), TOTAL_LABELS=length(Price))

 filtered <- df %>% select(Subtype, AVG_PRICE, MIN_PRICE, MAX_PRICE, AVG_ALCOHOL_CONTENT, TOTAL_LABELS)
          
          ggplot(data=filtered, aes(x=reorder(Subtype, TOTAL_LABELS), y=TOTAL_LABELS)) + 
            geom_bar(stat = "identity", colour="slateblue4", fill="lightblue", width=.7) + coord_flip() + 
            xlab("Available Subtype") + ylab("Total Labels")
```


--- 


## <h1 style="text-align:center;font-weight:bold">And another Output</h1> 
<br>
<br>


```{r, results="asis", echo=FALSE}
library(DT)

filtered <- thedf %>% select(Type, Name, Alcohol_Content, Price) %>% arrange(Alcohol_Content) %>% head(6)

print(xtable(filtered), type="html", html.table.attributes='class="mytable"')
```

<br>
To see more, go to https://github.com/roseapple0803/LiquorStore


